### 2018-04-05 reports/thesis/chapters/5_inference.tex
Added plotPValues method, added alternative example.

It can be shown that the BH procedure controls the FDR such that
\begin{equation}
    \text{FDR}\leqslant\pi_0\alpha\leqslant\alpha
\end{equation}
where $\pi_0=n_0/n$ \citep{benjamini1995controlling}, this is usually unknown in practice.

@@

A few numerical examples will be shown here to explore the properties of the 3 different types of method to do multiple hypothesis testing. Two scenarios will be shown here. In the first case. 1\,000 $\normal(0,1)$ test statistics are simulated, all test statistics are all null. In the second case, 800 null $\normal(0,1)$ and 200 alternative $\normal(2,1)$ test statistics were simulated.

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{../figures/inference/nullhisto.eps}
	\caption{A histogram of simulated of 1\,000 null test statistics. Also provided are the critical boundaries at the $z_\alpha=2$ level, one uncorrected for multiple testing, another corrected using the Bonferroni correction.}
	\label{fig:inference_nullhisto}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{../figures/inference/nullpvalues.eps}
	\caption{Ordered $p$-values of simulated 1\,000 null test statistics. Any values below the critical line are declared positive using the BH procedure.}
	\label{fig:inference_nullpvalues}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width = 0.7\textwidth]{../figures/inference/althisto.eps}
	\caption{A histogram of simulated of 800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ test statistics. Also provided are the critical boundaries at the $z_\alpha=2$ level using no correction, Bonferroni correction and the BH procedure.}
	\label{fig:inference_althisto}
\end{figure}

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/altpvalues.eps}
        \caption{All $p$-values}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/altpvalues_zoom.eps}
        \caption{Zoomed in}
    \end{subfigure}
    }
    \caption{Ordered $p$-values of simulated 800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ test statistics. Any values below the critical line are declared positive using the BH procedure.}
	\label{fig:altpvalues}
\end{figure}

@@

The error rates can be estimated as a result of knowing whenever each test statistic is truly null or non-null. Suppose the simulation was repeated $N$ times and $r_1,r_2,\dotdotdot,r_N$ test statistics were tested positive. From these positive results, suppose in addition that $v_1,v_2,\dotdotdot,v_N$ false positives were observed, following the notation in Table \ref{table:inference_randomvariables}. The error rates can be estimated
\begin{equation}
	\widehat{\text{PCER}} = \frac{1}{Nn}\sum_{i=1}^N v_i
\end{equation}
\begin{equation}
	\widehat{\text{FWER}} = \frac{1}{N} \sum_{i=1}^N \mathbb{I}(v_i\neq 0)
\end{equation}
\begin{equation}
	\widehat{\text{FDR}} = \frac{1}{N}\sum_{i=1}^N\dfrac{v_i}{r_i}\times\mathbb{I}(r_i\neq0)
	\ .
\end{equation}
The estimates of PCER and FDR is esentially the sample mean, so the standard error can be used to quantify the error. For the FWER, the variance of the Beta distribution is used to quantify the error
\begin{equation}
	\text{standard error of }\widehat{\text{FWER}} = 
	\sqrt{\dfrac{ab}{(a+b)^2(a+b+1)}}
\end{equation}
where $a = \sum_{i=1}^N \mathbb{I}(v_i\neq 0)$ and $b = N - a$.

@@

A $200\times200$ section of the $z$ image was investigated by plotting the histogram as shown in Figure \ref{fig:inference_sub_z}. One could simply use the BH procedure at the $z_\alpha=2$ level to get the critical region of $\|Z\|>\input{../figures/inference/sub_boundary.txt}...$. However a quick look at the histogram will show that almost half of the pixels will be tested as positive. It is questionable whenever such number of positive results is sensible, in particular in an area where defects are not expected.

@@

\cite{efron2004large} invented the empirical null to tackle problems observed in large scale multiple hypothesis testing, for example in microarrays \citep{hedenfalk2001gene, efron2002empirical, efron2003robbins}. These problems are similar to the one observed at the start of this chapter. The empirical null is now used widely, including in neuroimaging \citep{schwartzman2008false,schwartzman2009empirical}.

@@

The choice of the bandwidth $h$ is important for the kernel density estimator. It controls how smooth the kernel density estimator is, with higher values of $h$ producing smoother curves \citep{friedman2001elements}. Cross validation methods do exist \citep{bowman1984alternative, sheather2004density} but they can be computationally expensive. Another option are rules of thumb \citep{silverman1986density, sheather2004density} and are typically of the form
\begin{equation}
	h = bn^{-1/5}\times\text{min}\left(s_z,\text{iqr}_z/1.34\right)
\end{equation}
where $b=0.9$ \citep{silverman1986density}. This rule of thumb was developed with consideration of bimodal Normal distributions \citep{silverman1986density}. Other options include $b=1.06$ and $b=1.144$ to produce smoother curves \citep{sheather2004density}.

@@

In conclusion, a small bias added to the rule of thumb will improve the performance of the estimator $\widehat{\sigma}_0$. \cite{silverman1986density} pointed out that a smaller bandwidth should be used when in particular the distribution is bimodal, this is why \cite{silverman1986density} suggest the use of $b=0.9$ rather than $b=1.06$. Following from this, it was chosen that the intercept shall be added to Silverman's rule of thumb for the use in the empirical null
\begin{equation}
	h = 0.9n^{-1/5}\times\text{min}\left(s_z,\text{iqr}_z/1.34\right) + 0.16
	\ .
	\tag{\ref{eq:inference_ourruleofthumb}}
\end{equation}

>>>>

It can be shown that the BH procedure controls the FDR such that
\begin{equation}
    \text{FDR}\leqslant\pi_0\alpha\leqslant\alpha
\end{equation}
where $\pi_0=n_0/n$ \citep{benjamini1995controlling}, which is usually unknown in practice.

@@

A few numerical examples will be shown here to explore the properties of the 3 different types of methods to do multiple hypothesis testing. Two scenarios will be shown here. In the first case, 1\,000 $\normal(0,1)$ independent test statistics were simulated, all test statistics are all null. In the second case, 800 null $\normal(0,1)$ and 200 alternative $\normal(2,1)$ independent test statistics were simulated.

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{../figures/inference/nullhisto.eps}
	\caption{A histogram of simulated of 1\,000 null test statistics. Also provided are the critical boundaries at the $z_\alpha=2$ level, one uncorrected for multiple testing, another corrected using the Bonferroni correction.}
	\label{fig:inference_nullhisto}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{../figures/inference/nullpvalues.eps}
	\caption{Ordered $p$-values of simulated 1\,000 null test statistics. Any values below the critical line are declared positive using the BH procedure.}
	\label{fig:inference_nullpvalues}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width = 0.8\textwidth]{../figures/inference/althisto.eps}
	\caption{A histogram of simulated of 800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ test statistics. Also provided are the critical boundaries at the $z_\alpha=2$ level using no correction, Bonferroni correction and the BH procedure.}
	\label{fig:inference_althisto}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{../figures/inference/altpvalues.eps}
    \caption{Ordered $p$-values of simulated 800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ test statistics. Any values below the critical line are declared positive using the BH procedure.}
	\label{fig:altpvalues}
\end{figure}

@@

The error rates can be estimated as a result of knowing whenever each test statistic is truly null or non-null. Suppose the simulation was repeated $N$ times and $r_1,r_2,\dotdotdot,r_N$ number of test statistics were observed to be tested positive. From these positive results, suppose in addition that $v_1,v_2,\dotdotdot,v_N$ false positives were observed. In other words, they are realisations of the random variables defined in Table \ref{table:inference_randomvariables}. The error rates can be estimated
\begin{equation}
	\widehat{\text{PCER}} = \frac{1}{Nn}\sum_{i=1}^N v_i
\end{equation}
\begin{equation}
	\widehat{\text{FWER}} = \frac{1}{N} \sum_{i=1}^N \mathbb{I}(v_i\neq 0)
\end{equation}
\begin{equation}
	\widehat{\text{FDR}} = \frac{1}{N}\sum_{i=1}^N\dfrac{v_i}{r_i}\times\mathbb{I}(r_i\neq0)
	\ .
\end{equation}
The estimates of PCER and FDR is esentially the sample mean, so the standard error can be used to quantify the error. For the FWER, the variance of the Beta distribution is used to quantify the error
\begin{equation}
	\text{standard error of }\widehat{\text{FWER}} = 
	\sqrt{\dfrac{ab}{(a+b)^2(a+b+1)}}
\end{equation}
where $a = \sum_{i=1}^N \mathbb{I}(v_i\neq 0)$ and $b = N - a$.

@@

A $200\times200$ section of the $z$ image was investigated by plotting the histogram as shown in Figure \ref{fig:inference_sub_z}. One could simply use the BH procedure at the $z_\alpha=2$ level to get the critical region of $\|Z\|>\input{../figures/inference/sub_boundary.txt}...$. However a quick look at the histogram will show that almost half of the pixels will be tested as positive. It is questionable whether such number of positive results is sensible, in particular in an area where defects are not expected.

@@

\cite{efron2004large} was motivated to tackle problems observed in large scale multiple hypothesis testing, for example in microarrays \citep{hedenfalk2001gene, efron2002empirical, efron2003robbins}. These problems are similar to the one observed at the start of this chapter. The empirical null is now used widely, including in neuroimaging \citep{schwartzman2008false,schwartzman2009empirical}.

@@

The choice of the bandwidth $h$ is important for the kernel density estimator. It controls how smooth the kernel density estimator is, with higher values of $h$ producing smoother curves \citep{friedman2001elements}. Cross validation methods do exist \citep{bowman1984alternative, sheather2004density} but they can be computationally expensive. Rules of thumb \citep{silverman1986density, sheather2004density} can be used instead and are typically of the form
\begin{equation}
	h = bn^{-1/5}\times\text{min}\left(s_z,\text{IQR}_z/1.34\right)
\end{equation}
where $b=0.9$ \citep{silverman1986density}. This rule of thumb was developed with consideration of bimodal Normal distributions \citep{silverman1986density}. Other options include $b=1.06$ and $b=1.144$ to produce smoother curves \citep{sheather2004density}.

@@

In conclusion, a small bias added to the rule of thumb will improve the performance of the estimator $\widehat{\sigma}_0$. \cite{silverman1986density} pointed out that a smaller bandwidth should be used when in particular the distribution is bimodal, this is why \cite{silverman1986density} suggest the use of $b=0.9$ rather than $b=1.06$. Following from this, it was chosen that the intercept shall be added to Silverman's rule of thumb for the use in the empirical null
\begin{equation}
	h = 0.9n^{-1/5}\times\text{min}\left(s_z,\text{IQR}_z/1.34\right) + 0.16
	\ .
	\tag{\ref{eq:inference_ourruleofthumb}}
\end{equation}

\subsection{Further Discussion}

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/alt_empirical_z_image.eps}
        \caption{$z$ image}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/alt_empirical_z_image_2.eps}
        \caption{Sample from left}
    \end{subfigure}
    }
    \caption{$z$ image from comparing a scan with \texttt{aRTist}. A sub-sample containing a defect is shown. Highlighted in red are significant pixels.}
    \label{fig:inference_alt_empirical_z_image}
\end{figure}

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/alt_empirical_z_histo_null.eps}
        \caption{Histogram}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/alt_empirical_z_parzen.eps}
        \caption{Kernel density estimate}
    \end{subfigure}
    }
    \caption{Histogram and kernel density estimate of the $z$ statistics, taken from the sub-sample.}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{../figures/inference/alt_empirical_z_p_values.eps}
	\caption{Ordered $p$ values corrected for the empirical null.}
\end{figure}
